Text Is All You Need

### 2023-05-04 docs/hes_final/article.qmd
Use images for tables and rearrange images

We evaluated the models against a set of common performance metrics (see @tbl-best-max-metrics, @tbl-best-min-metrics, @fig-roc, @fig-prc). Despite conceptual differences in dataset creation and modeling techniques, all three of the described above approaches produced comparative results. Each of the models outperformed the other two in a subset of these metrics.

@@

::: {layout="[[1], [1]]"}

| metric               |   FFNN |   XGBoost |   Transformer |
|:---------------------|-------:|----------:|--------------:|
| False Discovery Rate |   0.73 |      0.83 |          0.80 |
| False Negative Rate  |   0.59 |      0.28 |          0.53 |
| False Positive Rate  |   0.19 |      0.51 |          0.30 |

: Model performance metrics (smaller values are better) {#tbl-best-min-metrics}

| metric             |   FFNN |   XGBoost |   Transformer |
|:-------------------|-------:|----------:|--------------:|
| Cohen Kappa Score  |   0.18 |      0.09 |          0.11 |
| F1 Score           |   0.33 |      0.28 |          0.28 |
| Precision Score    |   0.27 |      0.17 |          0.20 |
| Recall Score       |   0.41 |      0.72 |          0.47 |
| Roc Auc Score      |   0.67 |      0.69 |          0.64 |
| True Negative Rate |   0.81 |      0.49 |          0.70 |

: Model performance metrics (larger values are better) {#tbl-best-max-metrics}

>>>>

We evaluated the models against a set of common performance metrics (see @fig-best-max-metrics, @fig-best-min-metrics, @fig-roc, 
@fig-prc). Despite conceptual differences in dataset creation and modeling techniques, all three of the described above approaches 
produced comparative results. Each of the models outperformed the other two in a subset of these metrics.

@@

![Model performance metrics (larger values are better)](imgs/fig-best-max-metrics.png){#fig-best-max-metrics}

![Model performance metrics (smaller values are better)](imgs/fig-best-min-metrics.png){#fig-best-min-metrics}

:::
